The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-13 article.tex
added new drawing

\begin{figure}[]
\centering
\includegraphics[width=0.4\textwidth]{Path_comp_uncomp}
\caption{The left shows the uncompromised map made up of states avoiding some area and the right shows a compromised map where the states do cross the same area. In this case the state obtained from the particle filter mean, demonstrated in blue, would likely yield a more compromised probability}
\label{fig:compmaps}
\end{figure}

@@

Position and velocity are included in the state in order to make future conjectures about the behavior of the robot.

@@

In order to communicate between agents within the proximity range the wifi communication channel is analyzed. In order to keep the agent to agent principle we render the IP layer of communication unfit and to a more conservative approach of omitting the IP layer to the network stack.

>>>>

\begin{figure}[]
\centering
\includegraphics[width=0.4\textwidth]{Path_comp}
\caption{The left shows the uncompromised map made up of states avoiding some area while the right shows a compromised map where the states do cross the area. In this case the state obtained from the particle filter mean at the star would likely yield a more compromised probability}
\label{fig:compmaps}
\end{figure}

@@

We begin by defining our state and control in \autoref{abs_st_ctr_table}. Position and velocity are included in the state in order to make future conjectures about the behavior of the robot.

\begin{table}[] \label{abs_st_ctr_table} \caption{Implemented state and control}
\begin{center}
\begin{tabular}{|c|c|}
\hline
State & Control\\
\hline
$x,y,\theta,v_f,v_\theta$ & $a_f,a_\theta$\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

In order to keep the agent to agent principle we render the IP layer of communication unfit and utilize a more conservative approach of omitting the IP layer to the network stack.
